Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2024-09-06 supplement/supplement.qmd
updated supplemental materials with new non-preregistered analyses

To contextualize our confirmatory (preregistered) findings, we conducted twoexploratory (non-preregistered) analyses.
Below, we present the results of analyses exploring the associations between adversity and performance on the separate WM tasks using linear regression.
The other exploratory analyses, which were based on alternative SEM specifications, are presented in the supplemental materials.

@@

>>>>

To contextualize our confirmatory (preregistered) findings, we conducted three exploratory (non-preregistered) analyses.
First, we explored associations between adversity and performance on the separate WM tasks using linear regression.
Second, we constrained regression paths in the SEM to zero, as an alternative to the equivalence tests.
Third, we computed Bayes Factors for the equivalence tests.

## 3.1 Linear regression analyses

@@

## 3.2 Bayes Factors for equivalence tests

We calculated Bayes factors for the preregistered equivalence tests using the *bain* package [@hoijtink_2019].
We evaluated evidence in favor of the hypothesis that the regression coefficients fell within the equivalence bounds ($\beta$ ≤ -0.1 and $\beta$ ≥ 0.1)

Third, as a robustness check, we calculated Bayes factors for the preregistered equivalence tests using the *bain* package [@hoijtink_2019], in which we evaluated evidence in favor of the hypothesis that the effects fell within the equivalence bounds, relative to the hypothesis that the effects fell outside the equivalence bounds.
The results are summarized in Table S3.
For all but one association, the model comparisons showed at least strong evidence in favor of the hypothesis that the effects fell within the equivalence bounds (BF~10~ ranging between `r BF_expl04 |> filter(Hypothesis != '-0.1 ≤ (WM capacity ~ Threat) ≥ 0.1') |> pull(BF.c) |> min()` and `r BF_expl04 |> filter(Hypothesis != '-0.1 ≤ (WM capacity ~ Threat) ≥ 0.1') |> pull(BF.c) |> max()`.
The only exception was the association between threat and WM capacity, for which we found moderate evidence for the hypothesis that the effect fell within the equivalence bounds (BF~10~ = `r BF_expl04 |> filter(Hypothesis == '-0.1 ≤ (WM capacity ~ Threat) ≥ 0.1') |> pull(BF.c)`.
Thus, these results were inconsistent with the preregistered frequentist equivalent tests.

```{r}
table_s3 <- BF_expl04 |> 
  select(Hypothesis, BF.c) |>
  flextable::flextable() |>
  compose(i = 1, j = 2, as_paragraph("BF", as_sub('10')), part = "header") %>%
  border_remove() %>% 
  add_header_row(
    values = " ",
    colwidths = 2
  ) |> 
  flextable::compose(
    i = 1, j = 1, 
    as_paragraph(as_b("Table S3. "), "Bayes Factors for practical equivalence tests."),
    part = "header"
  ) |> 
  add_footer_row(
    values = " ",
    colwidths = 2
  ) |> 
  flextable::compose(
    i = 1, j = 1, 
    as_paragraph("BF = Bayes factor; CV = coefficient of variance, INR = income-to-needs ratio, M = mean, Perc. Scarcity = perceived scarcity, WM = working memory"), 
    part = "footer"
  ) |> 
  border(i = 1, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 2, border.bottom = fp_border_default(), part = "header") %>% 
  border(i = 10, border.bottom = fp_border_default(), part = "body") %>% 
  autofit()

table_s3
```
